Harmony: A Verifiable Systems Programming Language

### 2022-01-16 paper/paper.tex

\documentclass[twocolumn]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{etoolbox}
\usepackage{paralist}
% \usepackage{bold-extra}
\usepackage{xcolor}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=violet]{hyperref}

@@

Harmony's unique combination of features are a familiar and easy
to learn high-level programming language, the ability to concisely
specify an interface, the ability to compare behaviors of specification
and implementation, the ability to modularly model check programs,
and support for dynamic memory allocation, continuations, and
interrupts.  In addition, Harmony finds various common problems
automatically without a complicated property specification language,
such as Harmony's ability to find instances of undesirable busy
waiting.

@@

Harmony is heavily based on Python to reduce the learning curve for
users.  Many of Python's powerful constructs and operators are
supported, including comprehensions.  Harmony does
not support classes and instead supports memory allocation and
pointers in a way that is familiar to C programmers.  While this
perhaps seems like a step back in language evolution, many
synchronization algorithms in the literature explicitly consider
memory accesses, and this has been a bonus for
analyzing such algorithms with Harmony.  Moreover, the Harmony model
checker can be used to check for memory leaks or access to dangling
pointers.

>>>>

\documentclass[twocolumn]{article}
\usepackage{usenix2019}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{tcolorbox}
\usepackage{verbatim}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{etoolbox}
\usepackage{paralist}
% \usepackage{bold-extra}
\usepackage{xcolor}
% \usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=violet]{hyperref}
\usepackage{hyperref}

@@

Harmony's unique combination of features are a familiar and easy
to learn high-level and highly expressive programming language, the
ability to concisely specify an interface, the ability to compare
behaviors of specification and implementation, the ability to
modularly model check programs, and support for dynamic memory
allocation, continuations, and interrupts.  In addition, Harmony
finds various common problems automatically without a complicated
property specification language, such as Harmony's ability to find
instances of undesirable busy waiting.

@@

Harmony is heavily based on Python to reduce the learning curve for
users.  Many of Python's powerful constructs and operators are
supported, including sets, lists, tuples, dictionaries, and
comprehensions.  In certain cases Harmony goes further than Python,
for example by allowing sets of dictionaries (Harmony does not have
so-called ``unhashable types'').

Harmony does not
support classes and instead supports memory allocation and pointers
in a way that is familiar to C programmers.  While this perhaps
seems like a step back in language evolution, many synchronization
algorithms in the literature explicitly consider memory accesses,
and this has been a bonus for analyzing such algorithms with Harmony.
Moreover, the Harmony model checker can be used to check for memory
leaks or access to dangling pointers.
